```{r}
library(readr)
friends_episodes_v3 <- read_csv("/home/vlad/Textbooks/3rd year/Data analysis/Labs/lab5/friends_episodes_v3.csv")
```

```{r}
library(psych)
describe(friends_episodes_v3)
head(friends_episodes_v3)
episodes <- friends_episodes_v3
```

```{r}
episodes$ep_number <- seq.int(nrow(episodes))
```

```{r}
library(ggplot2)
library(dplyr)
ts(episodes)
ggplot(episodes, aes(x=episodes$ep_number, y=episodes$Stars)) + geom_line() + xlab("Episode number") + ylab("Star rating")

```

```{r}
require(smooth)
require(Mcomp)
sma(episodes$Stars, order=3, silent=F)
sma(episodes$Stars, order=5, silent=F)
sma(episodes$Stars, order=7, silent=F)
```
```{r}
TS <- ts(data = episodes$Stars, start = 1, frequency = 24) 
plot(decompose(TS))
TS %>% ggtsdisplay()
```

```{r}
library(tseries)
adf.test(TS)
```


```{r}
hw = HoltWinters(TS, alpha = 0.05, beta = 0.05, gamma = 0.05)
p = predict(hw, 50, prediction.interval = F)
plot(hw, p, xlab="Епізод", ylab="Рейтинг",
main="Прогноз за методом Холта-Вінтерса")
```
```{r}
AIC(arima(TS, order = c(1, 0, 1), seasonal=c(1, 0, 1)))
```
```{r}
AIC(arima(TS, order = c(1,0,1), seasonal=c(1, 0, 2)))
```
```{r}
library(forecast)
fit <- arima(TS, order = c(1, 0, 1), seasonal=c(1, 0, 2))
```

```{r}
library(ggplot2)
#fit %>% forecast(h = 8) %>% autoplot()
```


```{r}
library(astsa)
sarima(TS,1,2,8,2,2,2,24)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
